\chapter{\texorpdfstring{\Acl{pwa}}{Partial-wave analysis}}
\label{chap:theory}

    The partial-wave decomposition is a standard technique in scattering theory.
    It allows to write down the scattering probability amplitude in terms of Legendre polynomials, the eigenvectors of the angular momentum operator, each representing a partial\index{partial wave} wave~\cite[\S~11.2]{griffiths_intro_qm}.


    In this chapter, I will show how to perform a \ac{pwa}\index{partial-wave analysis} of a heavy-meson decay to disentangle the various contributions to the decay amplitude.
    I will focus on the isobar decomposition of a spinless parent particle to three pseudo-scalar spinless daughter particles in the final state.
    This is the case of the $\PDplus\to\Ppiplus\Ppiminus\Ppiplus$ decay, to which I will refer throughout the whole thesis.


    In the last part of the chapter, I will briefly introduce the reader to the Dalitz plot, a particularly useful visualization tool in \acp{pwa} of three-body decays.

    \input{mainmatter/theory/the_isobar_decomposition.tex}
    \input{mainmatter/theory/dalitz-plot_analysis.tex}

    \section{Summary}

    In analyses of experimental data, one has to take into account the events coming from non-resonant interactions.
    This is done by summing an amplitude term to the decay amplitude~\eqref{eq:isobar_decomposition}:
    \begin{equation}
        \A_{\text{data}}(\tau) = \A(m_X;\tau) + a_{\text{NR}} \A_{\text{NR}}(\tau),
    \end{equation}
    where $a_{\text{NR}}$ is a complex coefficient, and $\A_{\text{NR}}$ a Lorentz-invariant function of the phase-space coordinate.
    Moreover, also the detector acceptance\index{acceptance} has to be taken into account.
    This is usually done by multiplying a function of the phase-space coordinate, $\epsilon(\tau)$, to the data intensity:
    \begin{equation}
        \Intensity_{\text{exp}}(\tau) = \epsilon(\tau)\,\abs{\A_{\text{data}}(\tau)}^2.
    \end{equation}
    In what follows, I will ignore the non-resonant contribution to the decay amplitude and the detector effects as I will only work on \ac{mc}-generated data.


    The decay amplitude that I will use in the rest of the thesis is equation~\eqref{eq:isobar_decomposition}, which has the following expansion:
    \begin{equation}
        \A(m_{\pi\pi}^2, m_{\pi\pi}^2) = \sum_{I} c_I \,\psi_{J_I}^{(\xi)\pi}\!(m_{\pi\pi}^2, m_{\pi\pi}^2)\, \mathcal{F}_{\!J_I}^{\PD}(q_{\xi\pi}^2(m_{\pi\pi}^2);R) \, \mathcal{F}_{\!J_I}^{\xi}(q_{\pi\pi}^2(m_{\pi\pi}^2);R)\,\Delta_I(m_{\pi\pi}^2).
    \end{equation}
    Please note that there is only one spin-dependent function for two sub-decays---namely, $\PDplus\to\xi\Ppiplus$ and $\xi\to\Ppiplus\Ppiminus$---because the functions~\eqref{eq:zemach_formalism} apply to three-body decays.
    Moreover, since the pions are spinless particles, their Blatt-Wei\ss{}kop factors are constant; and, since they are final-state particles, their dynamic shape is $\delta(s_{\pi}-m_{\pi}^2)$.
